---
title: 'Question 5: Volatility and GARCH estimates'
author: "Andrew Hyde"
date: '2022-11-26'
output:
  pdf_document: default
  html_document: default
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, fig.width = 6, fig.height = 5, fig.pos="H", fig.pos = 'H')
# Note: Include = FALSE implies the code is executed, but not printed in your pdf.
# warning and message = FALSE implies ugly messages and warnings are removed from your pdf.
# These should be picked up when you execute the command chunks (code sections below) in your rmd, not printed in your paper!

# Lets load in example data, and see how this can be stored and later called from your 'data' folder.

cncy <- read_rds("data/currencies.rds")
cncy_Carry <- read_rds("data/cncy_Carry.rds")
cncy_value <- read_rds("data/cncy_value.rds")
cncyIV <- read_rds("data/cncyIV.rds")
bbdxy <- read_rds("data/bbdxy.rds")


```


<!-- ############################## -->
<!-- # Start Writing here: -->
<!-- ############################## -->

# Introduction \label{Introduction}

Using the currency data set (all relative to the USD) - I want you to comment on the following
statements:

The South African rand (ZAR) has over the past few years been one of the most volatile
currencies;

The ZAR has generally performed well during periods where G10 currency carry trades
have been favourable and these currency valuations relatively cheap. Globally, it has been
one of the currencies that most benefit during periods where the Dollar is comparatively
strong, indicating a risk-on sentiment.

Use your discretion on what you use to measure volatility, which currencies you compare
and how you arrive at your conclusions. Be creative in using tables, graphs and statistics to
argue your points.

```{r}



```

## Q5.1
The South African rand (ZAR) has over the past few years been one of the most volatile
currencies.

Currency Implied Volatility (cncyIV), similar to the construction of the VIX index. Currency Implied Volatility uses both put and call option premiums to gauge the market's forward implied volatility of the currency. A higher value indicates the market foresees higher future volatility for a currency.

Making use of the Currency Implied Volatility data, I arrange the currencies in descending order of volatility.
```{r}

# Table of 20 most volatile stocks according to average volatility over 
Q5.1_vol_table_func(df_data = df_q5.1_cncyIV_data)

```

Plot the volatility of Top 5 most volatile

```{r}

Q5.1_graph_func_vol(df_data = df_q5.1_cncyIV_graph_data,
                    title = "Currency Implied Volatility per Country",
                    subtitle = "Top 10 Most Volatile",
                    caption = "Data Source:",
                    xlabel = "Year",
                    ylabel = "Implied Volatility")

```
From the table and graph, RSA currency appears to be the most volatile.


##  Q5.2

The ZAR has generally performed well during periods where G10 currency carry trades
have been favourable and these currency valuations relatively cheap. Globally, it has been
one of the currencies that most benefit during periods where the Dollar is comparatively
strong, indicating a risk-on sentiment.



We use the Deutsche Bank G10 Harvest Index (DBHVG10U) as the proxy for the returns of a carry
strategy.This index reflects the return of being long the 3 high-yielding currencies
against being short the 3 low-yielding currencies within the G10 currency universe.
The index is rebalanced quarterly. Every quarter the currencies are re-ranked
according to their current 3-month Libor rate. The Bloomberg code for this factor is
DBHVG10U Index



