---
# IMPORTANT: Change settings here, but DO NOT change the spacing.
# Remove comments and add values where applicable.
# The descriptions below should be self-explanatory

title: "Question 4: Volatility Comparison"
#subtitle: "This will appear as Right Header"

documentclass: "elsarticle"

# --------- Thesis title (Optional - set to FALSE by default).
# You can move the details below around as you please.
Thesis_FP: FALSE
# Entry1: "An unbelievable study with a title spanning multiple lines."
# Entry2: "\\textbf{Nico Katzke}" # textbf for bold
# Entry3: "A thesis submitted toward the degree of Doctor of Philosophy"
# Uni_Logo: Tex/Logo.png # Place a logo in the indicated location (from your root, e.g. defaults to ~/Tex/Logo.png) and uncomment this line. Leave uncommented for no image
# Logo_width: 0.3 # If using a logo - use this to set width (size) of image
# Entry4: "Under the supervision of: \\vfill Prof. Joe Smith and Dr. Frank Smith"
# Entry5: "Stellenbosch University"
# Entry6: April 2020
# Entry7:
# Entry8:

# --------- Front Page
# Comment: ----- Follow this pattern for up to 5 authors
AddTitle: TRUE # Use FALSE when submitting to peer reviewed platform. This will remove author names.
Author1: "Andrew Hyde"  # First Author - note the thanks message displayed as an italic footnote of first page.
Ref1: "Stellenbosch University, South Africa" # First Author's Affiliation
Email1: "23365935\\@sun.ac.za" # First Author's Email address

# Author2: "John Smith"
# Ref2: "Some other Institution, Cape Town, South Africa"
# Email2: "John\\@gmail.com"
# CommonAffiliation_12: TRUE # If Author 1 and 2 have a common affiliation. Works with _13, _23, etc.
# 
# Author3: "John Doe"
# Email3: "Joe\\@gmail.com"
# 
# CorrespAuthor_1: TRUE  # If corresponding author is author 3, e.g., use CorrespAuthor_3: TRUE
# 
# # Comment out below to remove both. JEL Codes only given if keywords also given.
# keywords: "Multivariate GARCH \\sep Kalman Filter \\sep Copula" # Use \\sep to separate
# JELCodes: "L250 \\sep L100"

# ----- Manage headers and footers:
#BottomLFooter: $Title$
#BottomCFooter:
#TopLHeader: \leftmark # Adds section name at topleft. Remove comment to add it.
BottomRFooter: "\\footnotesize Page \\thepage" # Add a '#' before this line to remove footer.
addtoprule: TRUE
addfootrule: TRUE               # Use if footers added. Add '#' to remove line.

# --------- page margins:
margin: 2.3 # Sides
bottom: 2 # bottom
top: 2.5 # Top
HardSet_layout: TRUE # Hard-set the spacing of words in your document. This will stop LaTeX squashing text to fit on pages, e.g.
# This is done by hard-setting the spacing dimensions. Set to FALSE if you want LaTeX to optimize this for your paper.

# --------- Line numbers
linenumbers: FALSE # Used when submitting to journal

# ---------- References settings:
# You can download cls format here: https://www.zotero.org/ - simply search for your institution. You can also edit and save cls formats here: https://editor.citationstyles.org/about/
# Hit download, store it in Tex/ folder, and change reference below - easy.
bibliography: Tex/ref.bib       # Do not edit: Keep this naming convention and location.
csl: Tex/harvard-stellenbosch-university.csl # referencing format used.
# By default, the bibliography only displays the cited references. If you want to change this, you can comment out one of the following:
#nocite: '@*' # Add all items in bibliography, whether cited or not
# nocite: |  # add specific references that aren't cited
#  @grinold2000
#  @Someoneelse2010

# ---------- General:
RemovePreprintSubmittedTo: TRUE  # Removes the 'preprint submitted to...' at bottom of titlepage
Journal: "Journal of Finance"   # Journal that the paper will be submitting to, if RemovePreprintSubmittedTo is set to TRUE.
toc: FALSE                       # Add a table of contents
numbersections: TRUE             # Should sections (and thus figures and tables) be numbered?
fontsize: 11pt                  # Set fontsize
linestretch: 1.2                # Set distance between lines.
link-citations: TRUE            # This creates dynamic links to the papers in reference list.

### Adding additional latex packages:
# header-includes:
#    - \usepackage{colortbl} # Add additional packages here.

output:
  pdf_document:
    keep_tex: TRUE
    template: Tex/TexDefault.txt
    fig_width: 3.5 # Adjust default figure sizes. This can also be done in the chunks of the text.
    fig_height: 3.5
abstract: |
  Abstract to be written here. The abstract should not be too long and should provide the reader with a good understanding what you are writing about. Academic papers are not like novels where you keep the reader in suspense. To be effective in getting others to read your paper, be as open and concise about your findings here as possible. Ideally, upon reading your abstract, the reader should feel he / she must read your paper in entirety.
---

<!-- First: Set your default preferences for chunk options: -->

<!-- If you want a chunk's code to be printed, set echo = TRUE. message = FALSE stops R printing ugly package loading details in your final paper too. I also suggest setting warning = FALSE and checking for warnings in R, else you might find ugly warnings in your paper. -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, fig.width = 6, fig.height = 5, fig.pos="H", fig.pos = 'H')
# Note: Include = FALSE implies the code is executed, but not printed in your pdf.
# warning and message = FALSE implies ugly messages and warnings are removed from your pdf.
# These should be picked up when you execute the command chunks (code sections below) in your rmd, not printed in your paper!

# load functions
list.files('code/', full.names = T, recursive = T) %>% .[grepl('.R', .)] %>% as.list() %>% walk(~source(.))

# Lets load in example data, and see how this can be stored and later called from your 'data' folder.
library(tidyverse)
# import the data
T40 <- read_rds("data/T40.rds")
T40$Tickers <- gsub("SJ|Equity", "", T40$Tickers)


```


<!-- ############################## -->
<!-- # Start Writing here: -->
<!-- ############################## -->

# Introduction \label{Introduction}

The JSE further wants to understand the concentration and commonality of returns within the Top 40 indexes.

Using the Top 40 Index data from question 3, calculate the concentration of returns among the ALSI constituents (J200) by considering it from both a Principal Component Analysis (PCA) perspective as well as a rolling constituent correlation perspective.

In your answer, also use stratification of monthly volatility by calculating the J200 Index returns and comparing return source concentrations (PCA  and correlations) for periods of high market volatility specifically.

I begin testing the data for missing values (NA) and then plotting the data to see if there are any significant outliers.

```{r}

graph_q4.1_func(df_data = q4.1_data,
                title = "Returns of ALSI Weighted Indexes",
                subtitle = "From 2008 to 2022",
                caption = "ALSI (J200) 40 Indexes",
                xlabel = "Date",
                ylabel = "Returns")



```

Now winsorize the data by setting any return above 0.25% equal to 0.25% and create a weighted return column based on the J200 weights.
I also determine if there are missing values that will effect the results of my analysis and then the data is mean-centered.

The index weight column J200 and Index_Name column both have missing values, however this is nothing to be concerned about as this just implies that some stocks don't have weights as they were included in the Top 40 or will be in the future but are not included at present. There NAs in the Top 40 data can be set to zero.

```{r message=FALSE, warning=FALSE}

# determine if there are NA's in the data
missing_values_by_column <- colSums(is.na(T40))
T40["J200"][is.na(T40["J200"])] <- 0 

T40 <- T40 %>% 
    select(-J400) %>%
    # can also winsorize the data
    mutate(Return = ifelse(Return > 0.25, 0.25, ifelse(Return < -0.25, -0.25, Return))) %>%
    arrange(date) %>%
    group_by(Tickers) %>%
    mutate(Return = Return - mean(Return)) %>%
    mutate(weighted_return = J200*Return) %>% 
    ungroup() %>% 
    filter(date > first(date))
    #select(date, Tickers, weighted_return)


# Plot the clean data
graph_q4.2_func(df_data = q4.2_data,
                title = "Returns of ALSI Weighted Indexes",
                subtitle = "From 2008 to 2022",
                caption = "ALSI (J200) 40 Indexes",
                xlabel = "Date",
                ylabel = "Returns")



```

# PCA

I make use of the FactoMineR package to run my first PCA, however once I made the data wide missing values for the returns of certain equities in the index at specific dates. This may be because of listing and de-listing on a public exchange. I now use the impute function to replace missing values with using "Drawn_Distribution_Own" method, however this did not works and then moved on to replacing the missing values with the "Drawn_Distribution_Collective" method.

```{r}
library(FactoMineR)
library(factoextra)

# pca requires wide, numeric data: REMORE date for PCA
# data_T40_wide <- T40 %>% filter(date > lubridate::ymd(20080101)) %>% 
#     select(date, Tickers, weighted_return) %>% 
#     mutate(Return = weighted_return) %>% # rename for the impute_missing_value function
#         spread(Tickers, Return) %>% select(-date) 

# test for NA's since PCA func returned NA error
tibble:colSums(is.na(data_T40_wide))

return_mat_Quick = T40 %>%  
    mutate(Return = weighted_return) %>% 
    select(date, Tickers, Return) %>% 
    filter(date > lubridate::ymd(20080101)) %>% 
    spread(Tickers, Return)

# need date column for impute_missing_returns
pca_T40_data <- impute_missing_returns(return_mat = return_mat_Quick, 
                                       impute_returns_method = "Drawn_Distribution_Collective")
# pca requires wide, numeric data: REMORE date for PCA
pca_T40 <- PCA(pca_T40_data %>% select(-date), graph = FALSE)


factoextra::fviz_screeplot(pca_T40, ncp = 10)
# Contributions of variables on PC1

```


```{r}
factoextra::fviz_contrib(pca_T40, choice = "var", axes = 1, top = 40, fill = "darkorange")
```


```{r}

fviz_pca_var(pca_T40, col.var = "contrib", repel = T) + theme_minimal()

```

# calc rolling contributions with PerformanceAnalytics
or 
starification from prac 2 bonus







