---
title: 'Question 7: Portfolio Construction '
author: "Andrew Hyde"
date: '2022-11-26'
output:
  pdf_document: default
  html_document: default
---


```{r setup}

knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE,
                      fig.width = 6, fig.height = 5, fig.pos="H", fig.pos ='H')
# Note: Include = FALSE implies the code is executed, but not printed in your pdf.
# warning and message = FALSE implies ugly messages and warnings are removed from your pdf.
# These should be picked up when you execute the command chunks (code sections below) in your rmd, not printed in your paper!


# load packages
pacman::p_load("tidyverse", "devtools", "rugarch", "rmgarch", 
    "forecast", "tbl2xts", "lubridate", "PerformanceAnalytics", 
    "ggthemes", "ks")
library(PortfolioAnalytics)
library(TTR)
pacman::p_load("DEoptim", "ROI", "ROI.plugin.glpk", "ROI.plugin.quadprog")


# load functions
list.files('code/', full.names = T, recursive = T) %>%
    .[grepl('.R', .)] %>% as.list() %>% walk(~source(.))


# load data, and see how this can be stored and later called from your 'data' folder.
MAA <- read_rds("data/MAA.rds")
MAA$Ticker <- gsub(" Index", "", MAA$Ticker)
msci <- read_rds("data/msci.rds") %>%
    filter(Name %in% c("MSCI_ACWI", "MSCI_USA", "MSCI_RE", "MSCI_Jap"))

```

# Introduction

To construct the portfolio using the PortfolioAnalytics package. I take into consideration the constraints on and requirements of the portfolio. I follow the vignette called 'Introduction to PortfolioAnalytics' by Ross Bennett, one of the package authors, and the package documentation to optimize this portfolio.

# Data

I then use the 'TTR' package to calculate returns for the combined data and filter the data for the last 20 years. I pad the data by looking back a maximum of 5 days to fill in missing values, this adds to ensure that each asset included has at least 3 years’ of returns data.

I begin by join the two data sets and select tickers in order of asset class.

Col 1-3: Equity
Col 4-5: Currency
col 6-11: Bonds and Credit
Col 12: Commodity

```{r}


q7_data_combined <- left_join(msci %>% 
                        spread(Name, Price) %>%
                        select(date, MSCI_ACWI, MSCI_Jap, MSCI_USA),
                    
                        MAA %>% select(-Name) %>% spread(Ticker, Price) %>%
            # Place in order of asset class
    
                    select(date, ADXY, DXY, 
        LP05TREH, LEATTREU, LGAGTRUH, LGCPTRUH, LUAGTRUU, LUACTRUU,
        BCOMTR),
        
                  by = "date")

# col 1-3: Equity
# col 4-5: Currency
# col 6-11: Bonds and Credit
# col 12: Commodity


q7_returns_data <- q7_data_combined %>% arrange(date) %>% 
    mutate(across(.cols = -date, 
                  .fns = ~TTR::ROC(.,
                    type = c("continuous", "discrete")[2])))%>% 
# Equivalent to:   # mutate_at(.vars = vars(-Date), ~./lag(.)-1) %>% 
    mutate_at(.vars = vars(-date), ~na.locf(., na.rm = F, maxgap = 5)) %>%
    # Pad NA's back max 5 days: 
    filter(date >= as.Date("2002-10-29")) %>%  # data for the last 20 years
    # convert into a xts
    tbl_xts()



```

# Creating the Portfolio Object

I optimize each portfolio subject to the constraints below.

Requirements:
Long-only strategy
When using covariance and mean forecasts, use a look-back of less than 3 years
Do not hold any assets with less than 3 years’ returns data
Apply Quarterly Re-balancing
Limit exposure to Bonds and credit instruments at 25%
Limit exposure to Equities at 60%
Limit single asset exposure at 40%

```{r}
set.seed(123)

fund.names <- colnames(q7_returns_data)

pspec <- portfolio.spec(assets=fund.names)


```

# Setting up the porfolio

Initially I use the random sample method to optimize the portfolio. However, this produced different results each time the same code was run, even after using 'set.seed()'. I then opted for the ROI optimization method to solve each portfolio.

I create three different portfolios, the first two subject to asset exposure constraints and the last without asset exposure constraints. I proceed to run optimization on the four portfolios to Minimize Risk, Maximize Return and then Minimize Riks without constraints. All positions in each portfolio is long only and all funds are invested (no cash holdings). Each portfolio is re-balance quartely and makes use of a rolling window = 90 days periods to calculate annulized returns.

# Minimize Risk

```{r}
# Adding Constraints to the Portfolio Object


# Long-only strategy, no short positions
pspec_3 <- add.constraint(portfolio=pspec, type="long_only")

# Assumed no cash is being held in the portfolio, therefore porfolio is under full investment
pspec_3 <- add.constraint(portfolio=pspec_3, 
                        type="weight_sum",
                        min_sum=0.99,
                        max_sum=1.01)


# Limit single asset exposure at 40%
pspec_3 <- add.constraint(portfolio=pspec_3,
                        type="box",
                        min=0.0,
                        max=0.4)

# Group Constraint
# Limit exposure to Bonds and credit instruments at 25%
# Limit exposure to Equities at 60%

pspec_3 <- add.constraint(portfolio=pspec_3, type="group",
                        groups=list(groupA=c(1, 2, 3), # Equities
                        groupB=c(6, 7, 8, 9, 10, 11, 12)), #Bonds and credit instruments
                        
                        group_min=c(0, 0),
                        group_max=c(0.4, 0.25))


# Adding Objectives


# When using covariance and mean forecasts, use a look-back of less than 3 years
# Do not hold any assets with less than 3 years’ returns data
# Apply Quarterly Rebalancing


#Portfolio Return Objective
# Optimiser

minrisk  <- add.objective(portfolio=pspec_3, type='risk', name='ETL')
# Using the
opt_minrisk <- optimize.portfolio.rebalancing(R = q7_returns_data, 
                            portfolio = minrisk,
                            optimize_method = "ROI",
                            search_size = 100, 
                            trace = T,
                            rp = NULL, # random portfolios passed into the function to                                  prevent recalculation
                            rebalance_on = "quarters", 
                            training_period = NULL, #number of periods to use as a training                               data in the front of the returns data

                            rolling_window = 90) # number of periods

print(opt_minrisk)


```

# Maximise Return

```{r}

# Adding Constraints to the Portfolio Object


# Long-only strategy, no short positions
pspec <- add.constraint(portfolio=pspec, type="long_only")

# Assumed no cash is being held in the portfolio, therefore porfolio is under full investment
pspec <- add.constraint(portfolio=pspec, 
                        type="weight_sum",
                        min_sum=0.99,
                        max_sum=1.01)


# Limit single asset exposure at 40%
pspec <- add.constraint(portfolio=pspec,
                        type="box",
                        min=0.0,
                        max=0.4)

# Group Constraint
# Limit exposure to Bonds and credit instruments at 25%
# Limit exposure to Equities at 60%

pspec_2 <- add.constraint(portfolio=pspec, type="group",
                        groups=list(groupA=c(1, 2, 3), # Equities
                        groupB=c(6, 7, 8, 9, 10, 11, 12)), #Bonds and credit instruments
                        
                        group_min=c(0, 0),
                        group_max=c(0.4, 0.25))


# Adding Objectives


# When using covariance and mean forecasts, use a look-back of less than 3 years
# Do not hold any assets with less than 3 years’ returns data
# Apply Quarterly Rebalancing

#Portfolio Risk Objective
# pspec <- add.objective(portfolio=pspec, 
#                        type='risk', 
#                        name='ETL',
#                        arguments=list(p=0.95))

#Portfolio Return Objective
pspec <- add.objective(portfolio=pspec,
                       type='return',
                       name='mean')


# Solver
# generate an arbitary number of constrained random portfolios

maxret <- random_portfolios(portfolio=pspec, 
                         permutations=100, 
                         rp_method='sample')

# Optimiser

maxret <- add.objective(portfolio=pspec, type="return", name="mean")
# Using the
opt_maxret <- optimize.portfolio.rebalancing(R = q7_returns_data, 
                            portfolio = maxret,
                            optimize_method = "ROI",
                            search_size = 100, 
                            trace = T,
                            rp = NULL, # random portfolios passed into the function to                                  prevent recalculation
                            rebalance_on = "quarters", 
                            training_period = NULL, #number of periods to use as a training                               data in the front of the returns data

                            rolling_window = 90) # number of periods

print(opt_maxret)


```

# Minimize Risk without Asset Exposure Constraints 

```{r}
# Adding Constraints to the Portfolio Object


# Long-only strategy, no short positions
pspec_4 <- add.constraint(portfolio=pspec, type="long_only")

# Assumed no cash is being held in the portfolio, therefore porfolio is under full investment
pspec_4 <- add.constraint(portfolio=pspec_4, 
                        type="weight_sum",
                        min_sum=0.99,
                        max_sum=1.01)



# Adding Objectives


# When using covariance and mean forecasts, use a look-back of less than 3 years
# Do not hold any assets with less than 3 years’ returns data
# Apply Quarterly Rebalancing

#Portfolio Risk Objective
# pspec <- add.objective(portfolio=pspec, 
#                        type='risk', 
#                        name='ETL',
#                        arguments=list(p=0.95))

#Portfolio Return Objective
# Optimiser

pspec_4 <- add.objective(portfolio=pspec_4 , type='risk', name='ETL')
# Using the
opt_no_constraints <- optimize.portfolio.rebalancing(R = q7_returns_data, 
                            portfolio = pspec_4,
                            optimize_method = "ROI",
                            search_size = 100, 
                            trace = T,
                            rp = NULL, # random portfolios passed into the function to                                  prevent recalculation
                            rebalance_on = "quarters", 
                            training_period = NULL, #number of periods to use as a training                               data in the front of the returns data

                            rolling_window = 90) # number of periods
print(opt_no_constraints)


```

# Discussion of Annualized Portfolio Results

# Minimize Risk
Asset exposure constraints with the objective of minimize risk, led to lower returns than if were to both minimize risk and maximize return, but a similar degree of risk.

Annualized Portfolio Rebalancing Return: 0.01790729
Annualized Portfolio Standard Deviation: 0.04286854

# Mamimize Return
Asset exposure constraints with the objective of maximize return, led to higher returns compared to any of the other portfolio objectives. However, this type of optimization leads to a more than double increase in the risk calculated by standard deviation.

Annualized Portfolio Rebalancing Return: 0.06223531
Annualized Portfolio Standard Deviation: 0.1020928

# Minimize Risk without Asset Exposure Constraints 
The portfolio with no asset exposure constraints that where I minimize risk, provides higher returns than the same portfolio subject to constraints but with a very similar level of risk. 

Annualized Portfolio Rebalancing Return: 0.02433584
Annualized Portfolio Standard Deviation: 0.04374746



# Visualisation of Portfolios

For the risk minimized and return maximized portfolios with asset exposure constraints, the graphs below show the breakdown of weights as they adjust over time. For the risk minimized portfolio we can see large exposure to Asian and American currencies, this makes sense as the currencies of the two largest trading countries by GDP would be very stable given that many assets are Dollar denominated. Whereas the return maximizing Portfolio is weights equities and bonds exposure more heavily to achieve higher returns.

```{r}
chart.Weights(opt_minrisk, main = "Risk Minimized Portfolio: Rebalancing Weights")

# ls(opt_minrisk)
# opt_minrisk[[5]] %>% tail(1)
# extractStats()
# weights_opt_minrisk <- extractWeights(opt_minrisk)
# weights_opt_minrisk %>% head(1)
# weights_opt_minrisk %>% tail(1)
# extractObjectiveMeasures(opt_minrisk)

```

```{r}
chart.Weights(opt_maxret, main = "Return Maximizing Portfolio: Rebalancing Weights")

```

