---
# IMPORTANT: Change settings here, but DO NOT change the spacing.
# Remove comments and add values where applicable.
# The descriptions below should be self-explanatory

title: "Question 2: Yield Spread"
#subtitle: "This will appear as Right Header"

documentclass: "elsarticle"

# --------- Thesis title (Optional - set to FALSE by default).
# You can move the details below around as you please.
Thesis_FP: FALSE
# Entry1: "An unbelievable study with a title spanning multiple lines."
# Entry2: "\\textbf{Nico Katzke}" # textbf for bold
# Entry3: "A thesis submitted toward the degree of Doctor of Philosophy"
# Uni_Logo: Tex/Logo.png # Place a logo in the indicated location (from your root, e.g. defaults to ~/Tex/Logo.png) and uncomment this line. Leave uncommented for no image
# Logo_width: 0.3 # If using a logo - use this to set width (size) of image
# Entry4: "Under the supervision of: \\vfill Prof. Joe Smith and Dr. Frank Smith"
# Entry5: "Stellenbosch University"
# Entry6: April 2020
# Entry7:
# Entry8:

# --------- Front Page
# Comment: ----- Follow this pattern for up to 5 authors
AddTitle: TRUE # Use FALSE when submitting to peer reviewed platform. This will remove author names.
Author1: "Andrew Hyde"  # First Author - note the thanks message displayed as an italic footnote of first page.
Ref1: "Stellenbosch University, South Africa" # First Author's Affiliation
Email1: "23365935\\@sun.ac.za" # First Author's Email address

# Author2: "John Smith"
# Ref2: "Some other Institution, Cape Town, South Africa"
# Email2: "John\\@gmail.com"
# CommonAffiliation_12: TRUE # If Author 1 and 2 have a common affiliation. Works with _13, _23, etc.
# 
# Author3: "John Doe"
# Email3: "Joe\\@gmail.com"
# 
# CorrespAuthor_1: TRUE  # If corresponding author is author 3, e.g., use CorrespAuthor_3: TRUE
# 
# # Comment out below to remove both. JEL Codes only given if keywords also given.
# keywords: "Multivariate GARCH \\sep Kalman Filter \\sep Copula" # Use \\sep to separate
# JELCodes: "L250 \\sep L100"

# ----- Manage headers and footers:
#BottomLFooter: $Title$
#BottomCFooter:
#TopLHeader: \leftmark # Adds section name at topleft. Remove comment to add it.
BottomRFooter: "\\footnotesize Page \\thepage" # Add a '#' before this line to remove footer.
addtoprule: TRUE
addfootrule: TRUE               # Use if footers added. Add '#' to remove line.

# --------- page margins:
margin: 2.3 # Sides
bottom: 2 # bottom
top: 2.5 # Top
HardSet_layout: TRUE # Hard-set the spacing of words in your document. This will stop LaTeX squashing text to fit on pages, e.g.
# This is done by hard-setting the spacing dimensions. Set to FALSE if you want LaTeX to optimize this for your paper.

# --------- Line numbers
linenumbers: FALSE # Used when submitting to journal

# ---------- References settings:
# You can download cls format here: https://www.zotero.org/ - simply search for your institution. You can also edit and save cls formats here: https://editor.citationstyles.org/about/
# Hit download, store it in Tex/ folder, and change reference below - easy.
bibliography: Tex/ref.bib       # Do not edit: Keep this naming convention and location.
csl: Tex/harvard-stellenbosch-university.csl # referencing format used.
# By default, the bibliography only displays the cited references. If you want to change this, you can comment out one of the following:
#nocite: '@*' # Add all items in bibliography, whether cited or not
# nocite: |  # add specific references that aren't cited
#  @grinold2000
#  @Someoneelse2010

# ---------- General:
RemovePreprintSubmittedTo: TRUE  # Removes the 'preprint submitted to...' at bottom of titlepage
Journal: "Journal of Finance"   # Journal that the paper will be submitting to, if RemovePreprintSubmittedTo is set to TRUE.
toc: FALSE                       # Add a table of contents
numbersections: TRUE             # Should sections (and thus figures and tables) be numbered?
fontsize: 11pt                  # Set fontsize
linestretch: 1.2                # Set distance between lines.
link-citations: TRUE            # This creates dynamic links to the papers in reference list.

### Adding additional latex packages:
# header-includes:
#    - \usepackage{colortbl} # Add additional packages here.

output:
  pdf_document:
    keep_tex: TRUE
    template: Tex/TexDefault.txt
    fig_width: 3.5 # Adjust default figure sizes. This can also be done in the chunks of the text.
    fig_height: 3.5
abstract: |
  This analysis of the current yield spreads in the local bond market places the current high spreads into historical context.
---

<!-- First: Set your default preferences for chunk options: -->

<!-- If you want a chunk's code to be printed, set echo = TRUE. message = FALSE stops R printing ugly package loading details in your final paper too. I also suggest setting warning = FALSE and checking for warnings in R, else you might find ugly warnings in your paper. -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, fig.width = 6, fig.height = 5, fig.pos="H", fig.pos = 'H')
# Note: Include = FALSE implies the code is executed, but not printed in your pdf.
# warning and message = FALSE implies ugly messages and warnings are removed from your pdf.
# These should be picked up when you execute the command chunks (code sections below) in your rmd, not printed in your paper!

library(tidyverse)
list.files('code/', full.names = T, recursive = T) %>% .[grepl('.R', .)] %>% as.list() %>% walk(~source(.))


# Lets load in example data, and see how this can be stored and later called from your 'data' folder.
SA_bonds <- read_rds("data/SA_Bonds.rds")
BE_Infl <- read_rds("data/BE_Infl.rds")
bonds_2y <- read_rds("data/bonds_2y.rds")
bonds_10y <- read_rds("data/bonds_10y.rds")
usdzar <- read_rds("data/usdzar.rds")
ZA_Infl <- read_rds("data/ZA_Infl.rds")
IV <- read_rds("data/IV.rds")


```


<!-- ############################## --> 
<!-- # Start Writing here: -->
<!-- ############################## -->

# Introduction \label{Introduction}

Economists have recently pointed out that the current yield spreads in local mid to longer dated bond yields have since 2020 been the highest in decades.

# South African Bond Yields
I begin by viewing the data and determine if there are any missing values. I then plot the yields for bonds of differing maturities to visualize the spread between the 3 Month, 2 year and 10 Year South African bonds.

From the graph below, it does appear that the yield spreads in local mid to longer dated bond yields have have increased since 2020 when compare to historical spreads. The yield on the 3 year bond has decreased since 2015, this may be a reflection of anticipated interest rate cuts in the near future. An increase in interest rates would imply an increase in bond prices and thus yields would decrease.

```{r}

# colSums(is.na(sa_bonds_tidy))
# there are no missing values or NA's

graph_q2.1_func(df_data = df_q2.1_data,
                title = "South African Bond Yields",
                subtitle = "From 2000 to 2022",
                caption = "",
                xlabel = "Date",
                ylabel = "Yield")

```

To further investigate this topic I combine the available data for this question using 'left_join'. I make use of this combined data set to perform the rest analysis.

```{r}

q2_data_combined <- left_join(
        # JOIN us DATA
        bonds_10y %>% group_by(Name) %>% filter(Name == "US_10Yr") %>% ungroup() %>% select(-Name),
        bonds_2y %>% group_by(Name) %>% filter(Name == "US_2yr") %>% ungroup() %>% select(-Name),
        by = "date") %>%
    
        # JOIN SA DATA
        left_join(.,
                  SA_bonds %>% select(-SA_3M),
                  by = "date") %>%
        # JOIN THE VIX
        left_join(.,
                  IV %>% mutate(VIX = Price) %>% group_by(Name) %>% filter(Name == "VIX")
                  %>% ungroup() %>% select(-Name, -Price),
                  by = "date") %>%

        # JOIN US ZAR Exchnage Rate
        left_join(.,
                  usdzar %>% mutate(USDZAR = Price) %>% ungroup() %>% select(-Name, -Price),
                  by = "date") %>%

        # JOIN THE inflation data
        left_join(.,
                  BE_Infl %>% mutate(Infl_est = Price) %>% ungroup() %>% select(-Name, -Price),
                  by = "date")


```

Using the combined data set, I plot out the the yields on mid and long term South African Bonds from 2019 to 2022 to get an idea how the spreads have changed since the pandemic.

The graph below illustrates how bond how mid and long term bond yields have adjusted after the COVID-19 pandemic. It is not surprising that 2 year bond yields are down considerably since the pandemic first hit, this may be the result of investors anticipating monetary easing through lowered interest rates to combat the economic downturn of the pandemic. This can be seen with sharp dive on the 2 year bond late in 2020. Since then, the monetary authorities have been concerned with rising inflation and so interest rate hikes have been taking place, which explains the increases in the 2 year yields since late 2020.

```{r}

graph_q2.3_func(df_data = df_q2.3_data,
                title = "South African Mid and Long Bonds Yields",
                subtitle = "With 10 Year Break-even inflation estimate, from 2019 to 2022",
                caption = "",
                xlabel = "Date",
                ylabel = "Percentage (%)")

```

# Domestic and Foreign Yields

I construct line graph and use 'facet_wrap' to display each variable on its own axis. The graph shows the the mid to long term yield spread for both South Africa and the United States over time, as well as the prevailing interest rate at the time.

Over the past 5 years in both the local South African Bonds market and the US Bonds Market, the mid to long term yield spread has widen for both countries. However, as the RSA bond spread is larger it appears that capital is flowing into South Africa to invest 

```{r}

graph_q2.2_func(df_data = df_q2.2_data,
                title = "US and ZAR Bond Yield Spreads",
                subtitle = "10 Year (Long) and 2 year (Mid) spreads, from 2018 to 2022",
                caption = "The US Dollar RSA Rand exchange rate is plotted alongside yield spreads.",
                xlabel = "Date",
                ylabel = "")

```

```{r}

# to deetermine which countries are included in the data.
#bonds_10y %>% select(Name) %>% unique()
#bonds_2y %>% select(Name) %>% unique()

```

I then plot the the 10 and 2 year yield spread of BRICS Countries along with the VIX. I do this by calculating spreads for each country and then select for these spread for the combined data set. The CBOE Volatility Index has been added to the plot to provide of how yield spreads between mid and long term bonds for the BRICS countries are increasing as volatility expectations increase.

From the graph it appears that that there is a positive relationship between volatility in the equities market implied by the VIX (when looking at the VIX spike in early 2020) and the bond yield spreads. Additionally, it appears that the yield spread between the more developing BRICS countries (Brazil, India, South Africa) experiences a widening of the yield spread since the beginning of the pandemic.

```{r}

graph_q2.4_func(df_data = df_q2.4_data,
                title = "BRICS Bond Yield Spreads",
                subtitle = "10 Year (Long) and 2 year (Mid) spreads, from 2018 to 2022",
                caption = "The CBOE Volatily Index (VIX) is plotted alongside yield spreads.",
                xlabel = "Date",
                ylabel = "")


```



