---
# IMPORTANT: Change settings here, but DO NOT change the spacing.
# Remove comments and add values where applicable.
# The descriptions below should be self-explanatory

title: "Question 3: Portfolio Construction"
#subtitle: "This will appear as Right Header"

documentclass: "elsarticle"

# --------- Thesis title (Optional - set to FALSE by default).
# You can move the details below around as you please.
Thesis_FP: FALSE
# Entry1: "An unbelievable study with a title spanning multiple lines."
# Entry2: "\\textbf{Nico Katzke}" # textbf for bold
# Entry3: "A thesis submitted toward the degree of Doctor of Philosophy"
# Uni_Logo: Tex/Logo.png # Place a logo in the indicated location (from your root, e.g. defaults to ~/Tex/Logo.png) and uncomment this line. Leave uncommented for no image
# Logo_width: 0.3 # If using a logo - use this to set width (size) of image
# Entry4: "Under the supervision of: \\vfill Prof. Joe Smith and Dr. Frank Smith"
# Entry5: "Stellenbosch University"
# Entry6: April 2020
# Entry7:
# Entry8:

# --------- Front Page
# Comment: ----- Follow this pattern for up to 5 authors
AddTitle: TRUE # Use FALSE when submitting to peer reviewed platform. This will remove author names.
Author1: "Andrew Hyde"  # First Author - note the thanks message displayed as an italic footnote of first page.
# Ref1: "Stellenbosch University, South Africa" # First Author's Affiliation
# Email1: "23365935\\@sun.ac.za" # First Author's Email address
# 
# Author2: "John Smith"
# Ref2: "Some other Institution, Cape Town, South Africa"
# Email2: "John\\@gmail.com"
# CommonAffiliation_12: TRUE # If Author 1 and 2 have a common affiliation. Works with _13, _23, etc.
# 
# Author3: "John Doe"
# Email3: "Joe\\@gmail.com"
# 
# CorrespAuthor_1: TRUE  # If corresponding author is author 3, e.g., use CorrespAuthor_3: TRUE
# 
# # Comment out below to remove both. JEL Codes only given if keywords also given.
# keywords: "Multivariate GARCH \\sep Kalman Filter \\sep Copula" # Use \\sep to separate
# JELCodes: "L250 \\sep L100"

# ----- Manage headers and footers:
#BottomLFooter: $Title$
#BottomCFooter:
#TopLHeader: \leftmark # Adds section name at topleft. Remove comment to add it.
BottomRFooter: "\\footnotesize Page \\thepage" # Add a '#' before this line to remove footer.
addtoprule: TRUE
addfootrule: TRUE               # Use if footers added. Add '#' to remove line.

# --------- page margins:
margin: 2.3 # Sides
bottom: 2 # bottom
top: 2.5 # Top
HardSet_layout: TRUE # Hard-set the spacing of words in your document. This will stop LaTeX squashing text to fit on pages, e.g.
# This is done by hard-setting the spacing dimensions. Set to FALSE if you want LaTeX to optimize this for your paper.

# --------- Line numbers
linenumbers: FALSE # Used when submitting to journal

# ---------- References settings:
# You can download cls format here: https://www.zotero.org/ - simply search for your institution. You can also edit and save cls formats here: https://editor.citationstyles.org/about/
# Hit download, store it in Tex/ folder, and change reference below - easy.
bibliography: Tex/ref.bib       # Do not edit: Keep this naming convention and location.
csl: Tex/harvard-stellenbosch-university.csl # referencing format used.
# By default, the bibliography only displays the cited references. If you want to change this, you can comment out one of the following:
#nocite: '@*' # Add all items in bibliography, whether cited or not
# nocite: |  # add specific references that aren't cited
#  @grinold2000
#  @Someoneelse2010

# ---------- General:
RemovePreprintSubmittedTo: TRUE  # Removes the 'preprint submitted to...' at bottom of titlepage
Journal: "Journal of Finance"   # Journal that the paper will be submitting to, if RemovePreprintSubmittedTo is set to TRUE.
toc: FALSE                       # Add a table of contents
numbersections: TRUE             # Should sections (and thus figures and tables) be numbered?
fontsize: 11pt                  # Set fontsize
linestretch: 1.2                # Set distance between lines.
link-citations: TRUE            # This creates dynamic links to the papers in reference list.

### Adding additional latex packages:
# header-includes:
#    - \usepackage{colortbl} # Add additional packages here.

output:
  pdf_document:
    keep_tex: TRUE
    template: Tex/TexDefault.txt
    fig_width: 3.5 # Adjust default figure sizes. This can also be done in the chunks of the text.
    fig_height: 3.5
abstract: |
  Abstract to be written here.
---

<!-- First: Set your default preferences for chunk options: -->

<!-- If you want a chunk's code to be printed, set echo = TRUE. message = FALSE stops R printing ugly package loading details in your final paper too. I also suggest setting warning = FALSE and checking for warnings in R, else you might find ugly warnings in your paper. -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	fig.height = 5,
	fig.pos = "H",
	fig.width = 6,
	message = FALSE,
	warning = FALSE
)
# Note: Include = FALSE implies the code is executed, but not printed in your pdf.
# warning and message = FALSE implies ugly messages and warnings are removed from your pdf.
# These should be picked up when you execute the command chunks (code sections below) in your rmd, not printed in your paper!

library(tidyverse)
library(tbl2xts)
library(PortfolioAnalytics)
library(rmsfuns)
#Load Packages
pacman::p_load("tidyr", "tbl2xts","devtools","lubridate", "readr", "PerformanceAnalytics", "ggplot2", "dplyr")

# load functions
list.files('code/', full.names = T, recursive = T) %>% .[grepl('.R', .)] %>% as.list() %>% walk(~source(.))


# load data, and see how this can be stored and later called from your 'data' folder
library(tidyverse)
T40 <- read_rds("data/T40.rds")
RebDays <- read_rds("data/Rebalance_days.rds")


```


<!-- ############################## -->
<!-- # Start Writing here: -->
<!-- ############################## -->

# Introduction \label{Introduction}

Using the information on the ALSI (J200) and SWIX (J400) top 40 Indexes, write a brief
research report in Texevier where you:

Compare the SWIX and ALSI methodologies by looking at the performance of different
size indexes (large, mid and small caps), sector exposures and stock concentration over
time. Use your discretion in writing a short report highlighting differences in the return
profiles

# The Data
I make use of the function from the practical to impute missing returns

```{r message=FALSE, warning=FALSE}
    
#Using the impute_missing_returns function replace the NA with values from the same distribution
new_data_T40 <- impute_missing_returns(return_mat = T40 %>%
            select(date, Tickers, Return) %>%
            filter(date > lubridate::ymd(20080101)) %>% 
            spread(Tickers, Return),
            impute_returns_method = "Average") %>% 
            gather(Tickers, Return, -date)


T40_imputed <- left_join(T40 %>% select(-Return) %>%
                arrange(date) %>% group_by(Tickers),new_data_T40,
                            by = c("date", "Tickers"))

# neaten the data
T40_imputed$Tickers <- gsub("SJ|Equity", "", T40_imputed$Tickers)


```


# Stratification of Idexes
You may use stratification of data/usdzar.rds to provide insight into the different return profiles of both methodologies during different periods of currency performance and
volatility.

Here I reply on the courses practical notes. I begin by creating the index returns using this capped weight estimator using the tbl2xts framework. Begin by plotting the culumative returns for each index.

```{r message=FALSE, warning=FALSE}

graph_q3.1_func(df_data = T40_imputed,
                title = "Cumulative Returns of ALSI and SWIX Weighted Indexes",
                subtitle = "From 2008 to 2022",
                caption = "ALSI (J200) and SWIX (J400) top 40 Indexes",
                xlabel = "Date",
                ylabel = "Percentage %")

```

Break down cumulative returns by industry

```{r message=FALSE, warning=FALSE}

graph_q3.2_func(df_data = T40_imputed,
                title = "Cumulative Returns of ALSI and SWIX: Financials Sector",
                subtitle = "From 2008 to 2022",
                caption = "ALSI (J200) and SWIX (J400) top 40 Indexes",
                xlabel = "Date",
                ylabel = "Percentage %")

```


```{r message=FALSE, warning=FALSE}

graph_q3.3_func(df_data = T40_imputed,
                title = "Cumulative Returns of ALSI and SWIX: Industrials Sector",
                subtitle = "From 2008 to 2022",
                caption = "ALSI (J200) and SWIX (J400) top 40 Indexes",
                xlabel = "Date",
                ylabel = "Percentage %")


```



```{r message=FALSE, warning=FALSE}

graph_q3.4_func(df_data = T40_imputed,
                title = "Cumulative Returns of ALSI and SWIX: Resources Sector",
                subtitle = "From 2008 to 2022",
                caption = "ALSI (J200) and SWIX (J400) top 40 Indexes",
                xlabel = "Date",
                ylabel = "Percentage %")

```



# Capping Indexes
Answer the JSE’s question on applying capping to the indexes - in particular looking at
the impact different capping levels would have had on both the SWIX and ALSI (6% and
10%). Use data/Rebalance days.rds to identify the Rebalance Days during past quarterly rebalances.

```{r message=FALSE, warning=FALSE}

cum_returns_q3.5_func(df_data = RebDays,
                    title = "Cumulative Returns of Capped Weighted Indexes",
                      subtitle = "ALSI (10%) and SWIX (6%), from 2008 to 2022",
                      caption = "ALSI (J200) and SWIX (J400) top 40 Indexes",
                      xlabel = "Date",
                      ylabel = "Percentage %")  


```



```{r}
#--------------------------------------------------------------------------------
# Now, to map this across all the dates, we can use purrr::map_df as follows:
Capped_df_6percent <- 
    rebalance_col %>% 
    # Split our df into groups (where the groups here are the rebalance dates:
    group_split(RebalanceTime) %>% 
    # Apply the function Proportional_Cap_Foo to each rebalancing date:
    map_df(~Proportional_Cap_Func(., W_Cap = 0.06) ) %>% select(-RebalanceTime)


```







